Language Bias in a Multilingual Tweet Corpus

### 2018-07-17 paper.tex
Relevance judgments
Address

\hypersetup{pdfauthor={Dmitrijs Milajevs}}
\author[A]{\fnms{Dmitrijs} \snm{Milajevs}%
  \thanks{Corresponding Author: Dmitrijs Milajevs, Guest Researcher,
    100 Bureau Drive,
    Gaithersburg, MD 20899, USA%
    ;
    E-mail: dmitrijs.milajevs@nist.gov.}}
%\author[B]{\fnms{Second} \snm{Author}}
%and
%\author[B]{\fnms{Third} \snm{Author}

@@

The topics are:\footnotemark{}
\footnotetext{The topic file is available as \sfile{topics.json.txt}.}
\begin{itemize}
\item \texttt{LV001:} \textbf{Latvia 100} \ The Centennial Celebration of the Republic of Latvia.
\item \texttt{LV002:} \textbf{Ice Hockey} \ Ice hockey.
\item \texttt{LV003:} \textbf{Refugees} \ Refugee crisis in Europe, attitude to immigration and immigrants.
\item \texttt{LV004:} \textbf{Brexit} \ Withdrawal of the United Kingdom from the European Union known as Brexit.
\item \texttt{LV005:} \textbf{Olympics} \ The Olympic games and the Latvian team.
\item \texttt{LV006:} \textbf{Winter} \ Winter, snow and cold weather.
\item \texttt{LV007:} \textbf{May 4} \ The Restoration of Independence Day.
\item \texttt{LV008:} \textbf{May 8-9} \ Remembrance of the end of Word War II (May 8). It is also honored as the Victory Day on May 9. The Europe Day is observed on May 9. Tweets about any of the three events are relevant.
\item \texttt{LV009:} \textbf{Midsummer} \ Midsummer celebration on June 23-24.
\item \texttt{LV010:} \textbf{November 11} \ A memorial day for soldiers who fought for the independence of Latvia.
\item \texttt{LV011:} \textbf{November 18} \ Proclamation Day of the Republic of Latvia.
\item \texttt{LV012:} \textbf{Christmas} \ Christmas.
\item \texttt{LV013:} \textbf{New Year} \ New Year.
\item \texttt{LV014:} \textbf{March 16} \ Remembrance Day of the Latvian legionnaires.\footnotemark{}
\item \texttt{LV015:} \textbf{The Chronicles of Melanie} \ Mel\=anijas Hronika (The Chronicles of Melanie) is a Latvian movie that was selected for the Foreign-Language Category for Oscars.
\item \texttt{LV006:} \textbf{Blizzard of Souls} \ A Latvian movie Dv\=ese\c{l}u Putenis (Blizzard of Souls) that is in production by the time of writing.
\end{itemize}

>>>>

\hypersetup{pdfauthor={Dmitrijs Milajevs}}
\author[A]{\fnms{Dmitrijs} \snm{Milajevs}%
  \thanks{Corresponding Author: Dmitrijs Milajevs
    %, Guest Researcher,
    %100 Bureau Drive,
    %Gaithersburg, MD 20899, USA%
    %;
    E-mail: dmitrijs.milajevs@nist.gov.}}
%\author[B]{\fnms{Second} \snm{Author}}
%and
%\author[B]{\fnms{Third} \snm{Author}

@@

The topics are:\footnotemark{}%
\footnotetext{The topic file is available as \sfile{topics.json.txt}. Relevance judgments are available as \sfile{relevance\_judgments.csv}.}%
\begin{itemize}
\item \texttt{LV001:} \textbf{Latvia 100} \ The Centennial Celebration of the Republic of Latvia.
\item \texttt{LV002:} \textbf{Ice Hockey} \ Ice hockey.
\item \texttt{LV003:} \textbf{Refugees} \ Refugee crisis in Europe, attitude to immigration and immigrants.
\item \texttt{LV004:} \textbf{Brexit} \ Withdrawal of the United Kingdom from the European Union known as Brexit.
\item \texttt{LV005:} \textbf{Olympics} \ The Olympic games and the Latvian team.
\item \texttt{LV006:} \textbf{Winter} \ Winter, snow and cold weather.
\item \texttt{LV007:} \textbf{May 4} \ The Restoration of Independence Day.
\item \texttt{LV008:} \textbf{May 8-9} \ Remembrance of the end of Word War II (May 8). It is also honored as the Victory Day on May 9. The Europe Day is observed on May 9. Tweets about any of the three events are relevant.
\item \texttt{LV009:} \textbf{Midsummer} \ Midsummer celebration on June 23-24.
\item \texttt{LV010:} \textbf{November 11} \ A memorial day for soldiers who fought for the independence of Latvia.
\item \texttt{LV011:} \textbf{November 18} \ Proclamation Day of the Republic of Latvia.
\item \texttt{LV012:} \textbf{Christmas} \ Christmas.
\item \texttt{LV013:} \textbf{New Year} \ New Year.
\item \texttt{LV014:} \textbf{March 16} \ Remembrance Day of the Latvian legionnaires.\footnotemark{}
\item \texttt{LV015:} \textbf{The Chronicles of Melanie} \ Mel\=anijas Hronika (The Chronicles of Melanie) is a Latvian movie that was selected for the Foreign-Language Category for Oscars.
\item \texttt{LV006:} \textbf{Blizzard of Souls} \ A Latvian movie Dv\=ese\c{l}u Putenis (Blizzard of Souls) that is in production by the time of writing.
\end{itemize}
